Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-03-27 Multiresolution_framework/ltx/manuscript.tex
minor edits

To demonstrate the MRAIDE estimation framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear. Note that there is a difference between forward and inverse modeling when making these assumptions. For example, by using a linear activation function in the estimator we are not assuming that there is necessarily a linear relationship between the membrane voltage and firing rate, but that the statistics of the neural masses fall within a linear operating region over the estimation time period. The major benefit of modeling the relationship between the mean membrane potential and firing rate is the ability to apply the EM algorithm. \dean{The loss in model accuracy may be offset estimation accuracy. }

It is important to point out there is no doubt that there will always be a mismatch between neural mass models and actual cortical tissue. Nevertheless, the simplifications used in formulating the equations enable the development of new methods for extracting information from electrophysiological data, that has the potential to influence the treatment of diseases such as epilepsy. The trade-off between parsimony and complexity is always difficult when considering neurodynamics and this is further complicated when using estimation algorithms that have huge computational demands with such high-dimensional systems.

>>>>

To demonstrate the MRAIDE estimation framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear. Note that there is a difference between forward and inverse modeling when making these assumptions. For example, by using a linear activation function in the estimator we are not assuming that there is necessarily a linear relationship between the membrane voltage and firing rate, but that the statistics of the neural masses fall within a linear operating region over the estimation time period. The major benefit of modeling the relationship between the mean membrane potential and firing rate is the ability to apply the EM algorithm. The loss in model accuracy may be offset estimation accuracy.

It is important to point out there is no doubt that there will always be a mismatch between neural field models and actual cortical tissue. Nevertheless, the simplifications used in formulating the equations enable the development of new methods for extracting information from electrophysiological data, that has the potential to influence the treatment of diseases such as epilepsy. The trade-off between parsimony and complexity is always difficult when considering neurodynamics and this is further complicated when using estimation algorithms that have huge computational demands with such high-dimensional systems.
